Formalizing the Edmonds-Karp Algorithm

### 2016-03-05 paper/root.tex
Fixed layout problem with sample proof
Fixed matrix order

  We implement nodes as natural numbers less than an upper bound $N$, and residual graphs are implemented by their capacity matrices, which, in turn,
  are realized as arrays of size $N*N$ with row-major indexing.
  The adjacency map of the network is implemented as an array of lists of nodes. 
  An augmenting path is represented by a list of edges, \ie a list of pairs of nodes.

>>>>

  We implement nodes as natural numbers less than an upper bound $N$, and residual graphs are implemented by their capacity matrices, which, in turn,
  are realized as arrays of size $N*N$ with row-major indexing, such that the successors of a node are close together in memory.
  The adjacency map of the network is implemented as an array of lists of nodes. 
  An augmenting path is represented by a list of edges, \ie a list of pairs of nodes.
